Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-08-08 scagnostics.Rmd
final smoothing

\textcolor{red}{A comparison between these indexes for the purpose of variable selection was discussed in @Grimm2016, and can be summarised as follows. The scagnostics measures are flexible and calculating the full set of measures provides useful guidance in variable selection, however they are found to be highly sensitive to outlying points and sample size (as a consequence of the binning). Both splines2D and dcor2D are found to be robust in this respect, but splines2D is limited to functional dependence, while dcor2D is found to take large values only in scenarios with large linear correlation. Finally the mutual information based index functions are found to be flexible, but are sensitive to the sample size and often take relatively large values also when no association is present. A comparison of MIC and dcor2D was also presented in @2014arXiv1401.7645S.}

\textcolor{red}{In addition to the seven indexes described above, we will also consider the holes index included in the `tourr` package, see [@CBC93,@Cook:2007:IDG:1557227]. This serves as a benchmark, demonstrating the desired behaviour. The index takes maximum values for a central hole distribution, and we rescale the values as described in the appendix such that values close to zero are found for normal distributions.}

>>>>

\textcolor{red}{A comparison between these indexes for the **purpose of variable selection**, but not projection pursuit, was discussed in @Grimm2016, and is summarised as follows. The scagnostics measures are flexible and calculating the full set of measures provides useful guidance in variable selection, however they are found to be highly sensitive to outlying points and sample size (as a consequence of the binning). Both splines2D and dcor2D are found to be robust in this respect, but splines2D is limited to functional dependence, while dcor2D is found to take large values only in scenarios with large linear correlation. The mutual information based index functions are found to be flexible, but are sensitive to the sample size and often take relatively large values even when no association is present. A brief comparison of MIC and dcor2D was also provided in @2014arXiv1401.7645S.}

\textcolor{red}{In addition to the seven indexes described above, we will also consider the holes index included in the `tourr` package, see [@CBC93,@Cook:2007:IDG:1557227]. This serves as a benchmark, demonstrating some desired behaviour. The index takes maximum values for a central hole in the sample distribution.}
